\tool: Revisiting BadUSB with Type-C

### 2021-03-21 WOOT/Files/experiment.tex
something

\textbf{Setup.}
%\fengwei{I would suggest to add references for devices such as
%Pi, ATMEGA32U4 board, Yamazawa, etc.}
As mentioned in Section~\ref{sec:badusb},
our \tool only requires common components that are easily accessible online or
in any electronic store. Here we choose the following parts to build a
prototype. To begin with, we choose the Raspberry Pi 4B~\cite{pi4b} as the embedded Single Board
Computer inside \tool, which is powerful enough to process video data and has
an onboard WiFi chip. As for the \ac{HID} Emulator, we use an Atmel ATMEGA32U4 board~\cite{atmel}
with \ac{USB} protocol support, which is able to emulate multiple \acp{HID}
with our modified firmware. About the \ac{USB} 3.x Hub, we use one from
UGREEN~\cite{ugreen}, which supports HDMI, \ac{USB} 2.0, and many other exported peripherals.
Apart from these essential parts, we also use an auxiliary power bank to
provide power for the Raspberry Pi and the mobile devices used by the victim.
The image of our \tool prototype can be found in Figure~\ref{fig:armory}.

@@

		During our experiment, we noticed that some devices did not mirror their screens to our \tool by default. In this case, \tool would inject a sequence of keystrokes to set the victim's device into mirror their screens. In both Windows 10 and Ubuntu (Gnome Desktop), \tool can inject `Win+P' (`Super' is another name for the `Win' key) to switch between different modes for external display. Figure~\ref{fig:ubuntu_switch} illustrates how these keystrokes works on Ubuntu and Windows 10 is similar. In MacOS, according to the official manual~\cite{appleman}, \tool can inject \mbox{`Command+F1'} keystroke to set the monitor into mirroring the primary screen. In EMUI, there is a special mode called `Desktop Mode', which allows users to use their smartphones like a desktop computer with an external screen. If this mode is victim's default setting, \tool can inject mouse movements to switch to mirror mode as \tool can obtain victim's `desktop' in this mode.

@@

In the experiment of HID emulator mode, we used {Lenovo Xiaoxin Pro 13
2020}, a PC with Windows 10 \mbox{(OS Build 18363.1379)} and Ubuntu 20.04.2 LTS with two \ac{USB} Type-C interfaces as the
target device. During this experiment, \tool disguised itself as a normal keyboard and an external screen as feedback channel. When first plugged in, the victim's devices raised a pop-up window asking victims what mode should the new screen be set to. \tool immediately injected a sequence of mouse movements and clicks to set itself as a mirror to the primary monitor. Thus we had successfully completed the attack initialization. Then we tested three scripts, ranging from reverse shell backdoor to malware payload execution, all of which resulted in success. Compared to original BadUSB attacks like Rubber Ducky, our \tool can provide attackers real-time feedback which allows attackers to perform more accurate attacks.
%This also warned us that we need more thorough defense against such BadUSB
%attack.

@@

After each experiment, the raw video and the corresponding \ac{OCR} result file was generated automatically, then we presented these files to him/her, introduced our attack, told him/her to analyze the video file and replace certain characters of the private data that appear in the \ac{OCR} result file with asterisks. This protects their privacy and is also a mark for us to confirm that the data we find contains their private data. At last, he/she would destroy all original files, leave only the desensitized \ac{OCR} results for us.
%\shuqing{Do we need to mention that agreement the conference required here?}
%\hongyi{I'm also quite concern about this.}

>>>>

\textbf{Setup.}
%\fengwei{I would suggest to add references for devices such as
%Pi, ATMEGA32U4 board, Yamazawa, etc.}
As mentioned in Section~\ref{sec:badusb},
our \tool only requires common components that are easily accessible online or
in any electronic store. Here we chose the following parts to build a
prototype. To begin with, we chose the Raspberry Pi 4B~\cite{pi4b} as the embedded Single Board
Computer inside \tool, which is powerful enough to process video data and has
an onboard WiFi chip. As for the \ac{HID} Emulator, we used an Atmel ATMEGA32U4 board~\cite{atmel}
with \ac{USB} protocol support, which is able to emulate multiple \acp{HID}
with our modified firmware. About the \ac{USB} 3.x Hub, we used one from
UGREEN~\cite{ugreen}, which supports HDMI, \ac{USB} 2.0, and many other exported peripherals.
Apart from these essential parts, we also used an auxiliary power bank to
provide power for the Raspberry Pi and the mobile devices used by the victim.
The image of our \tool prototype can be found in Figure~\ref{fig:armory}.

@@

		During our experiment, we noticed that some devices did not mirror their screens to our \tool by default. In this case, \tool would inject a sequence of keystrokes to set the victim's device into mirror their screens. In both Windows 10 and Ubuntu (Gnome Desktop), \tool can inject `Win+P' (`Super' is another name for the `Win' key) to switch between different modes for external display. Figure~\ref{fig:ubuntu_switch} illustrates how these keystrokes works on Ubuntu and Windows 10 is similar. In MacOS, according to the official manual~\cite{appleman}, \tool can inject \mbox{`Command+F1'} keystrokes to set the monitor into mirroring the primary screen. In EMUI, there is a special mode called `Desktop Mode', which allows users to use their smartphones like a desktop computer with an external screen. If this mode is victim's default setting, \tool can inject mouse movements to switch to mirror mode as \tool can obtain victim's `desktop' in this mode.

@@

In the experiment of HID emulator mode, we used {Lenovo Xiaoxin Pro 13
2020}, a PC with Windows 10 \mbox{(OS Build 18363.1379)} and Ubuntu 20.04.2 LTS with two \ac{USB} Type-C interfaces as the
target device. During this experiment, \tool disguised itself as a normal keyboard and an external screen as feedback channel. When first plugged in, the victim's device raised a pop-up window asking the victim which mode should the new screen be set to. \tool immediately injected a sequence of mouse movements and clicks to set itself as a mirror to the primary monitor. Thus we had successfully completed the attack initialization. Then we tested three scripts, ranging from reverse shell backdoor to malware payload execution, all of which resulted in success. Compared to original BadUSB attacks like Rubber Ducky, our \tool can provide attackers real-time feedback which allows attackers to perform more accurate attacks.
%This also warned us that we need more thorough defense against such BadUSB
%attack.

@@

After each experiment, the raw video and the corresponding \ac{OCR} result file was generated automatically, then we presented these files to him/her, introduced our attack, told him/her to analyze the video file and replace certain characters of the private data that appear in the \ac{OCR} result file with asterisks. This protects their privacy and is also a mark for us to confirm that the data we found contains their private data. At last, he/she would destroy all original files, leave only the desensitized \ac{OCR} results for us.
%\shuqing{Do we need to mention that agreement the conference required here?}
%\hongyi{I'm also quite concern about this.}

### 2021-03-21 WOOT/Files/related_work.tex
something

We survey related works on \ac{USB} attacks in Section~\ref{subsec:usb_attack} and
\ac{USB} security defense in Section~\ref{subsec:usb_defence}, respectively.

@@

% USB protocol attacks
In the field of \ac{USB} security, protocol masquerading is also a widely used
attack scheme. Due to the lack of authentication in the \ac{USB} protocol, malicious
devices can hide their real functionality with re-written
firmware~\cite{rubber,badusb,rubberducky2020,usbbypassing,iseeyou,usbdriver}.
These works rewrite the firmware of a normal-looking flash drive, which allows
it to act like other devices. When these modified drives are connected to the
host, they could be recognized as a keyboard or mouse. Then the attacker can
execute malicious payloads as they were using the victim's devices. Due to the
limitation of \ac{USB} 2.0~\cite{usb20} protocol, these BadUSB
attacks~\cite{badusb} are unable to obtain video feedback from the victim
as video stream was not supported until \ac{USB} 3.0~\cite{usb30}.

\ac{MHL} extends the \ac{USB} standard and allows the video signal to
be transmitted through the \ac{USB} interface even for \ac{USB} 2.0 protocol. 
JFA~\cite{JFC}, short for Juice Filming Attacks,
abuses this standard and monitoring the victim's device utilizing \ac{USB} 2.0 protocol. Although the JFA~\cite{JFC} could exfiltrates video data from the victim's device without permission,  
there are two main limitation compared with \tool: 
\ding{182} JFA~\cite{JFC} can only exfiltrate video data passively from the victim's device, while \tool can control the victim's device at the same time as monitoring the screen. All data can be collected by JFA only after the victim's interaction, while \tool can gather sensitive data actively through \ac{HID} injection. For example, if the victim leaves his/her phone charging without locking it, JFA cannot obtain anything in this case, while \tool can actively control his/her device and gather sensitive information.
\ding{183} The official list of \ac{MHL} Devices~\cite{MHLlist} shows that the latest mobile devices supporting \ac{MHL} were released in 2015, which indicates the lack of support of \ac{MHL} and limits the attack range of JFA. \tool attacks over \ac{USB} Type-C interface, the latest \ac{USB} connector designed to replace all previous USB connector including MicroUSB~\cite{li2018usb}. So \tool has a wider attack range.

% Using USB devices to inject code
Besides attacking from the protocol perspective, previous works\shuqing{re?} used a
\ac{USB} device as a payload delivery means. Duqu~\cite{duqu} uses a user-mode
rootkit to hide malicious files on the \ac{USB} storage device, Flame\cite{flame} uses a
zero-day exploit and malicious \textit{autorun.inf} to execute the malware
automatically. There are also works \cite{brain,stuxnet,conficker}
following the same paradigm and performing code-injection attacks. These
attacks are much more damaging and flexible,
but they require certain existing flaws like a zero-day vulnerability\cite{zero-day}  and \ac{USB} is merely
a payload delivery method.

@@

From the hardware perspective, the BadUSB attack requires \mbox{`D-' and `D+'} pins which
are defined by the protocol to transmit data. Without these pins, data cannot 
be transferred via a \ac{USB} cable. Based
on this fact, \ac{USB} Condom~\cite{Condom} is a hardware solution to block data
channels by adding a blocker in the connector. This blocker can cut off the \mbox{`D-' and `D+'} connection while leaving the power pins intact. However, this method poses
a great challenge to the \ac{PnP} property of \ac{USB}, as once it is deployed, it
stops all \ac{USB} functions other than charging.

@@

After the \ac{USB} enumeration and driver loading, some related works follow the \textit{defense in depth} approach to defend against BadUSB attacks.  
Neuner \emph{et al.}~\cite{neuner2018usblock}
prevent BadUSB attacks from the malicious flash drive by analyzing
the temporal characteristics of BadUSB-like attacks. This defense mechanism is
effective because the attacker cannot obtain the screen of the host using
BadUSB. In this case, the malicious device can only inject keystrokes in a very
short time to reduce the risk of being discovered. 
This property causes the
typing characteristics of BadUSB to be detectable. Pham \emph{et al.}~\cite{pham2010optimizing} optimize Windows security features, which can
block the execution of unsigned files and the installation of unsigned drivers
carried on portable media. Moreover, in GoodUSB, a VM is deployed in the host as
a honeypot to detect and stop malicious behavior of \ac{USB} devices.

>>>>

We surveyed related works on \ac{USB} attacks in Section~\ref{subsec:usb_attack} and
\ac{USB} security defense in Section~\ref{subsec:usb_defence}, respectively.

@@

% USB protocol attacks
In the field of \ac{USB} security, protocol masquerading is also a widely used
attack scheme. Due to the lack of authentication in the \ac{USB} protocol, malicious
devices can hide their real functionality with re-written
firmware~\cite{rubber,badusb,rubberducky2020,usbbypassing,iseeyou,usbdriver}.
These works rewrite the firmware of a normal-looking flash drive, which allows
it to act like other devices. When these modified drives are connected to the
host, they could be recognized as a keyboard or mouse. Then the attacker can
execute malicious payloads as they are using the victim's device. Due to the
limitation of \ac{USB} 2.0~\cite{usb20} protocol, these BadUSB
attacks~\cite{badusb} are unable to obtain video feedback from the victim
as video stream was not supported until \ac{USB} 3.0~\cite{usb30}.

\ac{MHL} extends the \ac{USB} standard and allows the video signal to
be transmitted through the \ac{USB} interface even for \ac{USB} 2.0 protocol. 
Juice Filming Attacks(JFA)~\cite{JFC},
abuses this standard and monitoring the victim's device utilizing \ac{USB} 2.0 protocol. Although the JFA~\cite{JFC} could exfiltrates video data from the victim's device without permission,  
there are two main limitation compared with \tool: 
\ding{182} JFA~\cite{JFC} can only exfiltrate video data passively from the victim's device, while \tool can control the victim's device at the same time as monitoring the screen. All data can be collected by JFA only after the victim's interaction, while \tool can gather sensitive data actively through \ac{HID} injection. For example, if a victim leaves his/her phone charging without locking it, JFA cannot obtain anything in this case, while \tool can actively control his/her device and gather sensitive information.
\ding{183} The official list of \ac{MHL} Devices~\cite{MHLlist} shows that the latest mobile devices supporting \ac{MHL} were released in 2015, which indicates the lack of support of \ac{MHL} and limits the attack range of JFA. \tool attacks over \ac{USB} Type-C interface, the latest \ac{USB} connector designed to replace all previous USB connector including MicroUSB~\cite{li2018usb}. So \tool has a wider attack range.

% Using USB devices to inject code
Besides attacking from the protocol perspective, previous works\shuqing{re?} use a
\ac{USB} device as a payload delivery means. Duqu~\cite{duqu} uses a user-mode
rootkit to hide malicious files on the \ac{USB} storage device, Flame\cite{flame} uses a
zero-day exploit and malicious \textit{autorun.inf} to execute the malware
automatically. There are also works \cite{brain,stuxnet,conficker}
following the same paradigm and performing code-injection attacks. These
attacks are much more damaging and flexible,
but they require certain existing flaws like a zero-day vulnerability\cite{zero-day}  and \ac{USB} is merely
a payload delivery method.

@@

From the hardware perspective, the BadUSB attack requires \mbox{(D+ \& D-)} pins which
are defined by the protocol to transmit data. Without these pins, data cannot 
be transferred via a \ac{USB} cable. Based
on this fact, \ac{USB} Condom~\cite{Condom} is a hardware solution to block data
channels by adding a blocker in the connector. This blocker can cut off the \mbox{(D+ \& D-)} connection while leaving the power pins intact. However, this method poses
a great challenge to the \ac{PnP} property of \ac{USB}, as once it is deployed, it
stops all \ac{USB} functions other than charging.

@@

After the \ac{USB} enumeration and driver loading, some related works follow the \textit{defense in depth} approach to defend against BadUSB attacks.  
Neuner \emph{et al.}~\cite{neuner2018usblock}
prevent BadUSB attacks from the malicious flash drive by analyzing
the temporal characteristics of BadUSB-like attacks. This defense mechanism is
effective because the attacker cannot obtain the screen of the victim host using
BadUSB. In this case, the malicious device can only inject keystrokes in a very
short time to reduce the risk of being discovered. 
This property causes the
typing characteristics of BadUSB to be detectable. Pham \emph{et al.}~\cite{pham2010optimizing} optimize Windows security features, which can
block the execution of unsigned files and the installation of unsigned drivers
carried on portable media. Moreover, in GoodUSB, a VM is deployed in the host as
a honeypot to detect and stop malicious behavior of \ac{USB} devices.
